Assistant Tools and Accessibility Features for Blind People Playing Visual-Centric Digital Games

### 2024-01-17 Paper/paper.tex
removed samples.ins + minor changes
Added minor structure of how I want to write my paper

	%%
	%% The "title" command has an optional parameter,
	%% allowing the author to define a "short title" to be used in page headers.
	\title{Assistant tools for blind people playing games}

@@

	\section{Introduction}
	%TODO
	Short summary of zelda cane article and what i want to expore more!

	\section{Related Work}
	%TODO
	Maybe short summary of the related works i gatherd (State of the art)

	\section{Conclusion}
	%TODO
	\cite{westland_cost_2002}

>>>>

	%%
	%% The "title" command has an optional parameter,
	%% allowing the author to define a "short title" to be used in page headers.
	\title{Assistant Tools and Accessibility Features for Blind People Playing Visual-Centric Digital Games}

@@

	\section{Introduction}
	%TODO
	Short summary of \emph{My Zelda Cane} paper about what they wrote and noting that they did not explore general Accessibility Features current game companies are using/developing as well as state-of-the-art tools.
	In Addition to that I want to explore those tools and Accessibility Features deeper.
	As Third point I want to get a deeper look into how software companies handle features for blind people like \emph{The Last of Us: Part 2}.

	\section{State of the art}
	%TODO
	New tools for blind players and newest Accessibility Features software companies using/developing.

	Screen Reader
	Audio Cues and Descriptions
	Haptic Feedback
	Customizable Controls
	Text-to-Speech and Speech Recognition
	Accessible Menus and Interfaces
	Echolocation

	\section{Get deeper into one or two new tools for blind players}
	%TODO

	\section{Get deeper into one or two Accessibility Features}
	%TODO

	\section{Future Work (What else could be done, explored deeper or would benefit blind players)}
	%TODO

	\section{Conclusion}
	%TODO
	Summary of key findings

	\cite{westland_cost_2002}
